Javelins with hyper3 objects

### 2022-04-18 inst/javelin.Rmd
javelin and attempts table work

```{r,label=loadjavelinandconvert}
a <- read.table("javelin.txt",header=TRUE)
a
o <- attemptstable2supp3(a,decreasing=TRUE,give.supp=FALSE)
o
```

@@

```{r,label=dothething1,cache=TRUE}    	   
H1 <- ordervec2supp3(v=names(o)[!is.na(o)],nonfinishers=names(o)[ is.na(o)])
m1 <- maxp(H1)
m1
```

```{r,label=dothething2,cache=TRUE}    	   
H2 <- ordervec2supp3(v=names(o)[!is.na(o)])
m2 <- maxp(H2)
m2
```

@@

>>>>

```{r,label=loadjavelinandconvert}
javelin_table <- read.table("javelin.txt",header=TRUE)
a <- javelin_table # saves typing

o <- attemptstable2supp3(a,decreasing=TRUE,give.supp=FALSE)
```

@@

```{r,label=dothething1,cache=TRUE}    	   
javelin <- attemptstable2supp3(a,decreasing=TRUE,give.supp=TRUE)
H1 <- javelin # saves typing
javelin1_maxp <- maxp(H1)
m1 <- javelin1_maxp
```

```{r,label=dothething2,cache=TRUE}    	   
H2 <- ordervec2supp3(v=names(o)[!is.na(o)])
javelin2_maxp  <- maxp(H2)
m2 <- javelin2_maxp
```

@@

### Package dataset {-}

Following lines create `javelin.rda`, residing in the `data/`
directory of the package.

```{r,label=savejavelindataset}
save(javelin,javelin_table,javelin1_maxp,javelin2_maxp,  file="javelin.rda")
```
